---
title: "Human health SQO assessment tool"
author: ""
output: 
  html_document
runtime: shiny
---

```{r setup, message = F, warning = F, echo = F}
library(knitr)
library(tidyverse)
library(shiny)
library(patchwork)
library(SQObioaccumulation)

opts_chunk$set(warning = FALSE, message = FALSE, eval = T, echo = F)

source('R/funcs.R')

# rmd downloads
downloadButtonRmd <- function (outputId, label = "Download", class = NULL, ...)  {
  tags$a(id = outputId, class = paste("btn btn-default shiny-download-link", 
                                      class), href = "", target = "_blank", download = NA, 
         icon("download"), label, ...)
}
```

```{r data}
# data inputs, lookups
tischmthr <- read.csv('data/tischmthr.csv', stringsAsFactors = FALSE)
finalsiteassess <- read.csv('data/finalsiteassess.csv', stringsAsFactors = FALSE)
indic_lookup <- read.csv('data/indic_lookup.csv', stringsAsFactors = FALSE)
biota_preyprop <- read.csv('data/preyprop.csv', stringsAsFactors = FALSE, row.names = 1)

# data inputs, with empty values to fill with user input
biotaemp <- read.csv('data/biota.csv', stringsAsFactors = FALSE)
constantsemp <- read.csv('data/constants.csv', stringsAsFactors = FALSE)
contamemp <- read.csv('data/contam.csv', stringsAsFactors = FALSE)
mcsparmsemp <- read.csv('data/mcsparms.csv', stringsAsFactors = F)

# indicator species lookup format for inputs
indic_lookup <- indic_lookup %>% 
  group_by(Indicator.number) %>% 
  nest %>% 
  deframe %>% 
  map(function(x) pull(x, Guild.species))
```

```{r}
# top controllers
column(12, 
  column(3, actionButton("run", "Run food web model!")), 
  column(3, actionButton("runmcs", "Run MC sims!")),
  column(2, h6('Number of MC sims')), 
  column(2, numericInput('nsim', NULL, value = 1000, min = 1, max = 20000))
)
```
<br></br>

Please see the [technical report](http://ftp.sccwrp.org/pub/download/DOCUMENTS/TechnicalReports/1000_SQOHumanHealthFramework.pdf) for complete documentation. 

```{r reactives}
res <- reactiveValues(cbiota = NULL, bsaf = NULL, contamcalc = NULL)

# run bioaccumulation model with inputs
observeEvent(input$run, 
  withProgress(
    message='Please wait',
    detail='Running bioaccumulation model...',
    value = 0, 
    {
         
      # input
      inptyp <- input$inptyp
      
      if(inptyp == 'Manual entry'){
        
        # format biota from input
        biota <- formsppinp(input, biotaemp)
      
        # format constants from input
        constants <- formcnsinp(input, constantsemp)
        
        # format contams from input
        contam <- formcntinp(input, contamemp)
        
      }
      
      if(inptyp == 'File upload'){
        
        # make sure all files are uploaded
        req(!is.null(input$biotaupl))
        req(!is.null(input$constantsupl))
        req(!is.null(input$contamupl))
        req(!is.null(input$mcsparmsupl))
        # validate(
        #   need(
        #     !any(
        #       is.null(input$biotaupl), 
        #       is.null(input$constantsupl), 
        #       is.null(input$contamupl),
        #       is.null(input$mcsparmsupl)
        #       ), 
        #     'Upload all files before running model'
        #   )
        # )
      
        biota <- read.csv(input$biotaupl$datapath, stringsAsFactors = F)
        constants <- read.csv(input$constantsupl$datapath, stringsAsFactors = F)
        contam <-  read.csv(input$contamupl$datapath, stringsAsFactors = F)
        
      }
      
      # calculated contaminant inputs
      contamcalc <- cntcalc(contam, constants)
    
      btch <- bioaccum_batch(biota, contamcalc, biota_preyprop, constants)
    
      # append to reactive output
      res$cbiota <- btch$cbiota
      res$bsaf <- btch$bsaf
      res$contamcalc <- contamcalc
  
    }
  )
)

# bsaf results
bsaf <- reactive({

  # input
  bsaf <-res$bsaf
  
  return(bsaf)
  
})

# concentration in biota
cbiota <- reactive({
  
  # input
  cbiota <- res$cbiota

  return(cbiota)
  
})

# summary of contaminants across indicator guilds
indic_sum <- reactive({
  
  # input
  cbiota <- cbiota()
  contamcalc <- res$contamcalc
  
  req(!is.null(res$contamcalc))

  out <- indic_sum_fun(cbiota, contamcalc)
  
  return(out)
  
})

# plot of bsaf and cbiota for selected contam
plobsaf <- reactive({
  
  # input
  bsaf <- bsaf()
  cbiota <- cbiota()
  cntbsaf <- input$cntbsaf
 
  req(cntbsaf)
  
  p <- plo_bsaf(bsaf, cbiota, cntbsaf)
  
  return(p)  
  
})

# table of bsaf and cbiota for all contaminants
tabbsaf <- reactive({
  
  # input
  bsaf <- bsaf()
  cbiota <- cbiota()
 
  req(bsaf)
  
  totab <- tab_bsaf(bsaf, cbiota)
  
  return(totab)
  
})

# get weighted average observed tissue concentrations from input, by contaminant category
wgtavg <- eventReactive(input$run, {

  # input
  inptyp <- input$inptyp
  
  # format mcs inputs
  if(inptyp == 'Manual entry'){
    mcsparms <- formmcsinp(input, mcsparmsemp)
  }
  if(inptyp == 'File upload'){
    mcsparms <- read.csv(input$mcsparmsupl$datapath, stringsAsFactors = F)
  }
  
  propseaf <- formpropseaf(input)

  out <- wgt_avg_fun(mcsparms, propseaf)

  return(out)
  
})

# run MCS to get site linkage values for nsim
MCSres <- eventReactive(input$runmcs,
  withProgress(
    message='Please wait',
    detail='Running simulations..',
    value = 0, {
    
      # validate from indic_sum
      validate(
        need(!is.null(res$contamcalc), "Run food web model before MCS!")
      )
    
      ##
      # inputs
      
      # number of sims
      nsim <- input$nsim
      inptyp <- input$inptyp
      
      # estimated tissue concentrations for site linkages
      indic_sum <- indic_sum()
    
      # format constants from input
      constants <- formcnsinp(input, constantsemp)
      
      # format seafood proportion of dieat
      propseaf <- formpropseaf(input)
      
      # format mcs inputs
      if(inptyp == 'Manual entry'){
        mcsparms <- formmcsinp(input, mcsparmsemp)
      }
      
      if(inptyp == 'File upload'){
        mcsparms <- read.csv(input$mcsparmsupl$datapath, stringsAsFactors = F)
      }
        
      ##
      # calcs
      out <- mcs_fun(nsim, indic_sum, mcsparms, constants, propseaf)
    
      return(out)
 
    }
  )
)

# site linkage plot from mcsres
mcspl <- reactive({
  
  # input
  MCSres <- MCSres()
  
  # plot
  p <- mcs_plo(MCSres)
  
  return(p)

})

# all mcs results long format
mcsres <- reactive({
  
  # input
  MCSres <- MCSres()
  
  totab <- MCSres %>% 
    spread(contam, sitsedlnk) 
  
  return(totab)

})

# summarize MCres to get percentiles of site linkage values
MCSsum <- reactive({
  
  # inputs
  MCSres <- MCSres()
  
  out <- mcs_sum_fun(MCSres)
  
  return(out)
  
})

# SQO assessment summary
sqosum <- reactive({
  
  # inputs
  MCSres <- MCSres()
  wgtavg <- wgtavg()
  
  out <- sqo_sum_fun(wgtavg, MCSres, tischmthr, constants, finalsiteassess)
  
  return(out)
  
})
```

```{r downloadhandlers}
# dl summary of contaminants across indicator guilds
output$dlindicsum <- downloadHandler(
  filename = function(){paste0(input$flprf, '_indicsum.csv')},
  content = function(file){
    write.csv(indic_sum(), file, quote = T, row.names = F)
  }
)

# dl plot for bsaf and cbiota for contaminant
output$dlplobsaf <- downloadHandler(
  filename = function(){paste0(input$flprf, '_', input$cntbsaf, '_plot.png')},
  content = function(file){
    png(file, width = 9, height = 7, family = 'serif', units = 'in', res = 250)
    print(plobsaf())
    dev.off()
  }
)

# dl table for bsaf and cbiota for all contaminants
output$dltabbsaf <- downloadHandler(
  filename = function(){paste0(input$flprf, '_allests.csv')},
  content = function(file){
    write.csv(tabbsaf(), file, quote = T, row.names = F)
  }
)

# dl table for sqo summary
output$dlsqosum <- downloadHandler(
  filename = function(){paste0(input$flprf, '_sqosum.csv')},
  content = function(file){
    write.csv(sqosum(), file, quote = T, row.names = F)
  }
)

# dl table for mcs summary
output$dlmcssum <- downloadHandler(
  filename = function(){paste0(input$flprf, '_mcssum.csv')},
  content = function(file){
    write.csv(MCSsum(), file, quote = T, row.names = F)
  }
)

# dl plot for mcs summary
output$dlmcspl <- downloadHandler(
  filename = function(){paste0(input$flprf, '_mcsplot.png')},
  content = function(file){
    png(file, width = 9, height = 7, family = 'serif', units = 'in', res = 250)
    print(mcspl())
    dev.off()
  }
)

# dl table for all mcs results
output$dlmcsres <- downloadHandler(
  filename = function(){paste0(input$flprf, '_mcsresults.csv')},
  content = function(file){
    write.csv(mcsres(), file, quote = T, row.names = F)
  }
)

# dl table for all calculated contaminants
output$dlcalccont <- downloadHandler(
  filename = function(){paste0(input$flprf, '_calccont.csv')},
  content = function(file){
    write.csv(res$contamcalc, file, quote = T, row.names = F)
  }
)

# dl biota template
output$dlbiotatmpl <- downloadHandler(
  filename = function(){paste0(input$flprf, '_biota.csv')},
  content = function(file){
    fl <- read.csv('data/inptmp/biota.csv', stringsAsFactors = F)
    write.csv(fl, file, quote = T, row.names = F)
  }
)

# dl constants template
output$dlconstantstmpl <- downloadHandler(
  filename = function(){paste0(input$flprf, '_constants.csv')},
  content = function(file){
    fl <- read.csv('data/inptmp/constants.csv', stringsAsFactors = F)
    write.csv(fl, file, quote = T, row.names = F)
  }
)

# dl contam template
output$dlcontamtmpl <- downloadHandler(
  filename = function(){paste0(input$flprf, '_contam.csv')},
  content = function(file){
    fl <- read.csv('data/inptmp/contam.csv', stringsAsFactors = F)
    write.csv(fl, file, quote = T, row.names = F)
  }
)

# dl mcsparms template
output$dlmcsparmstmpl <- downloadHandler(
  filename = function(){paste0(input$flprf, '_mcsparms.csv')},
  content = function(file){
    fl <- read.csv('data/inptmp/mcsparms.csv', stringsAsFactors = F)
    write.csv(fl, file, quote = T, row.names = F)
  }
)

```

# {.tabset}

## Model inputs 

```{r}
column(12,
  column(3, selectInput('inptyp', label = 'Select input type:', choices = c('Manual entry', 'File upload'), selected = 'File upload')),
  column(3, textInput('flprf', 'File prefix for downloads:', value = 'output1'))
)         
```

```{r}
output$entry <- renderUI({
  
  # inputs
  inptyp <- input$inptyp
  
  if(inptyp == 'Manual entry'){
    
    # splitlayout widths
    wds <- 100

    w1 <- wellPanel(id = "indicspec", style = "overflow-x:scroll; background-color:#daf1da",
    
      # headers 1
      fluidRow(
        column(3, renderText(NULL)),
        column(3, renderText(NULL)),
        column(2, renderText(NULL)),
        splitLayout(cellWidths = wds,
          renderText(NULL),
          h6('Chlordane (ng/g)'),
          renderText(NULL),
          h6('Dieldrin (ng/g)'),
          renderText(NULL),
          h6('DDT (ng/g)'),
          renderText(NULL),
          h6('PCB (ng/g)'),
          renderText(NULL)
        )
      ),

      # headers 2
      fluidRow(
        column(3, renderText(NULL)),
        column(3, h6('Select species')),
        column(2, h6('Portion seafood')),
        splitLayout(cellWidths = wds,
          h6('Lipid proportion'),
          h6('Mean'),
          h6('SE'),
          h6('Mean'),
          h6('SE'),
          h6('Mean'),
          h6('SE'),
          h6('Mean'),
          h6('SE')
        )
      ),

      # indic 1
      fluidRow(
        column(3, h6('1 Piscivore')),
        column(3, selectInput('indic1', NULL, choices = indic_lookup[['Indicator species 1']], selected = indic_lookup[['Indicator species 1']][1])
               ),
        column(2, numericInput('indic1seaf', NULL, value = 0, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic1lip', NULL, value = 0.0036, min = 0, max = 1, width = '100%'),
          numericInput('indic1ChlordaneX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic1ChlordaneSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic1DieldrinX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic1DieldrinSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic1DDTX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic1DDTSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic1PCBX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic1PCBSD', NULL, value = NULL, min = 0, width = '100%')
        )
      ),

      # indic 2
      fluidRow(
        column(3, h6('2 Benthic diet with piscivory')),
        column(3, selectInput('indic2', NULL, choices = indic_lookup[['Indicator species 2']], selected = indic_lookup[['Indicator species 2']][14])),
        column(2, numericInput('indic2seaf', NULL, value = 0.5, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic2lip', NULL, value = 0.0044, min = 0, max = 1, width = '100%'),
          numericInput('indic2ChlordaneX', NULL, value = 2.0425, min = 0, width = '100%'),
          numericInput('indic2ChlordaneSD', NULL, value = 0.909979488352973, min = 0, width = '100%'),
          numericInput('indic2DieldrinX', NULL, value = 0.25, min = 0, width = '100%'),
          numericInput('indic2DieldrinSD', NULL, value = 0, min = 0, width = '100%'),
          numericInput('indic2DDTX', NULL, value = 2.40733333333333, min = 0, width = '100%'),
          numericInput('indic2DDTSD', NULL, value = 1.30059647460184, min = 0, width = '100%'),
          numericInput('indic2PCBX', NULL, value = 71.0791428571429, min = 0, width = '100%'),
          numericInput('indic2PCBSD', NULL, value = 36.3098108973698, min = 0, width = '100%')
        )
      ),

      # indic 3
      fluidRow(
        column(3, h6('3 Benthic and pelagic with piscivory')),
        column(3, selectInput('indic3', NULL, choices = indic_lookup[['Indicator species 3']], selected = indic_lookup[['Indicator species 3']][6])),
        column(2, numericInput('indic3seaf', NULL, value = 0, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic3lip', NULL, value = 0.0158, min = 0, max = 1, width = '100%'),
          numericInput('indic3ChlordaneX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic3ChlordaneSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic3DieldrinX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic3DieldrinSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic3DDTX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic3DDTSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic3PCBX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic3PCBSD', NULL, value = NULL, min = 0, width = '100%')
        )
      ),

      # indic 4
      fluidRow(
        column(3, h6('4 Benthic without piscivory')),
        column(3, selectInput('indic4', NULL, choices = indic_lookup[['Indicator species 4']], selected = indic_lookup[['Indicator species 4']][10])),
        column(2, numericInput('indic4seaf', NULL, value = 0, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic4lip', NULL, value = 0.0329, min = 0, max = 1, width = '100%'),
          numericInput('indic4ChlordaneX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic4ChlordaneSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic4DieldrinX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic4DieldrinSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic4DDTX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic4DDTSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic4PCBX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic4PCBSD', NULL, value = NULL, min = 0, width = '100%')
        )
      ),

      # indic 5
      fluidRow(
        column(3, h6('5 Benthic and pelagic without piscivory')),
        column(3, selectInput('indic5', NULL, choices = indic_lookup[['Indicator species 5']], selected = indic_lookup[['Indicator species 5']][4])),
        column(2, numericInput('indic5seaf', NULL, value = 0.5, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic5lip', NULL, value = 0.0125, min = 0, max = 1, width = '100%'),
          numericInput('indic5ChlordaneX', NULL, value = 2.5275, min = 0, width = '100%'),
          numericInput('indic5ChlordaneSD', NULL, value = 0.4157433102288, min = 0, width = '100%'),
          numericInput('indic5DieldrinX', NULL, value = 0.25, min = 0, width = '100%'),
          numericInput('indic5DieldrinSD', NULL, value = 0, min = 0, width = '100%'),
          numericInput('indic5DDTX', NULL, value = 7.283, min = 0, width = '100%'),
          numericInput('indic5DDTSD', NULL, value = 2.51069636948402, min = 0, width = '100%'),
          numericInput('indic5PCBX', NULL, value = 1.9195, min = 0, width = '100%'),
          numericInput('indic5PCBSD', NULL, value = 0.976160911428029, min = 0, width = '100%')
        )
      ),

      # indic 6
      fluidRow(
        column(3, h6('6 Benthic with herbivory')),
        column(3, selectInput('indic6', NULL, choices = indic_lookup[['Indicator species 6']], selected = indic_lookup[['Indicator species 6']][1])),
        column(2, numericInput('indic6seaf', NULL, value = 0, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic6lip', NULL, value = 0.0356, min = 0, max = 1, width = '100%'),
          numericInput('indic6ChlordaneX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic6ChlordaneSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic6DieldrinX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic6DieldrinSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic6DDTX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic6DDTSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic6PCBX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic6PCBSD', NULL, value = NULL, min = 0, width = '100%')
        )
      ),

      # indic 7
      fluidRow(
        column(3, h6('7 Benthic and pelagic with herbivory')),
        column(3, selectInput('indic7', NULL, choices = indic_lookup[['Indicator species 7']], selected = indic_lookup[['Indicator species 7']][2])),
        column(2, numericInput('indic7seaf', NULL, value = 0, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic7lip', NULL, value = 0.0117, min = 0, max = 1, width = '100%'),
          numericInput('indic7ChlordaneX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic7ChlordaneSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic7DieldrinX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic7DieldrinSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic7DDTX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic7DDTSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic7PCBX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic7PCBSD', NULL, value = NULL, min = 0, width = '100%')
        )
      ),

      # indic 8
      fluidRow(
        column(3, h6('8 Pelagic with benthic herbivory')),
        column(3, selectInput('indic8', NULL, choices = indic_lookup[['Indicator species 8']], selected = indic_lookup[['Indicator species 8']][2])),
        column(2, numericInput('indic8seaf', NULL, value = 0, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic8lip', NULL, value = 0.0444, min = 0, max = 1, width = '100%'),
          numericInput('indic8ChlordaneX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic8ChlordaneSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic8DieldrinX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic8DieldrinSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic8DDTX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic8DDTSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic8PCBX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic8PCBSD', NULL, value = NULL, min = 0, width = '100%')
        )
      ),

      # indic 9
      fluidRow(
        column(3, h6('9 Benthic diet with piscivory: estuarine')),
        column(3, selectInput('indic9', NULL, choices = indic_lookup[['Indicator species 9']], selected = indic_lookup[['Indicator species 9']][1])),
        column(2, numericInput('indic9seaf', NULL, value = 0, min = 0, max = 1)),
        splitLayout(cellWidths = wds,
          numericInput('indic9lip', NULL, value = 0.0036, min = 0, max = 1, width = '100%'),
          numericInput('indic9ChlordaneX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic9ChlordaneSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic9DieldrinX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic9DieldrinSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic9DDTX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic9DDTSD', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic9PCBX', NULL, value = NULL, min = 0, width = '100%'),
          numericInput('indic9PCBSD', NULL, value = NULL, min = 0, width = '100%')
        )
      ),

      # sediment contaminant concentration
      fluidRow(
        column(6, h5('Sediment contaminant concentration')),
        # column(3, NULL),
        column(2, NULL),
        splitLayout(cellWidths = wds,
          renderText(NULL),
          numericInput('sedChlordaneX', NULL, value = 0.5, min = 0, width = '100%'),
          numericInput('sedChlordaneSD', NULL, value = 0, min = 0, width = '100%'),
          numericInput('sedDieldrinX', NULL, value = 0.5, min = 0, width = '100%'),
          numericInput('sedDieldrinSD', NULL, value = 0, min = 0, width = '100%'),
          numericInput('sedDDTX', NULL, value = 1.19166666666667, min = 0, width = '100%'),
          numericInput('sedDDTSD', NULL, value = 0.765187658537288, min = 0, width = '100%'),
          numericInput('sedPCBX', NULL, value = 1.33454545454546, min = 0, width = '100%'),
          numericInput('sedPCBSD', NULL, value = 1.60216108332035, min = 0, width = '100%')
        )
      )
      
    )

    w2 <- wellPanel(id = "envdat", style = "background-color:#daf1da",

      # site area
      fluidRow(
        column(4, h6('Area of site (km2)')),
        column(2, numericInput('SA', NULL, value = 8.06, min = 0, width = '100%'))
      ),

      # site length
      fluidRow(
        column(4, h6('Length of site (km)')),
        column(2, numericInput('SL', NULL, value = 6, min = 0, width = '100%'))
      ),

      # organic carb prop in sed (TOC)
      fluidRow(
        column(4, h6('Organic carbon in sediment (kg/kg)')),
        column(2, numericInput('ocsed', NULL, value = 0.0163, width = '100%'))
      ),

      # doc conc in water
      fluidRow(
        column(4, h6('DOC conc. in water (kg/L)')),
        column(2, numericInput('xdoc', NULL, value = 0.00000215, min = 0, width = '100%'))
      ),

      # poc conc in water
      fluidRow(
        column(4, h6('POC conc. in water (kg/L)')),
        column(2, numericInput('xpoc', NULL, value = 0.00000157, min = 0, width = '100%'))
      ),

      # water temp
      fluidRow(
        column(4, HTML('<h6>Mean water temperature (&deg;C)</h6>')),
        column(2, numericInput('T', NULL, value = 17.4, width = '100%'))
      ),

      # salinity
      fluidRow(
        column(4, h6('Water salinity (psu)')),
        column(2, numericInput('salinity', NULL, value = 25.4, min = 0, width = '100%'))
      ),

      # dissolved oxygen
      fluidRow(
        column(4, h6('Dissolved oxygen (mg/L)')),
        column(2, numericInput('Cox', NULL, value = 8.09, min = 0, width = '100%'))
      ),

      # concentration of suspended solids
      fluidRow(
        column(4, h6('Conc. of suspended solids (kg/L)')),
        column(2, numericInput('vss', NULL, value = 0.0000246, min = 0, width = '100%'))
      )

    )
    
    w3 <- wellPanel(id = "contamdat", style = "overflow-y:scroll; max-height: 300px; background-color:#daf1da",

      # headers
      fluidRow(
        column(2, NULL),
        column(2, NULL),
        column(2, 'Sediment (ng/g dry wt)'),
        column(2, 'Dissolved surface water (pg/L)'),
        column(2, 'Pore water (pg/L)')
      ),

      # Chlordane
      fluidRow(
      	column(2, h6('Chlordane')),
      	column(2, h6('alphaChlordane')),
      	column(2, numericInput('alphaChlordane_sed', NULL, value = 0.5, min = 0, width = '100%')),
      	column(2, numericInput('alphaChlordane_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('alphaChlordane_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # Chlordane
      fluidRow(
      	column(2, h6('Chlordane')),
      	column(2, h6('gammaChlordane')),
      	column(2, numericInput('gammaChlordane_sed', NULL, value = 0.5, min = 0, width = '100%')),
      	column(2, numericInput('gammaChlordane_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('gammaChlordane_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # Chlordane
      fluidRow(
      	column(2, h6('Chlordane')),
      	column(2, h6('alphaNonachlor')),
      	column(2, numericInput('alphaNonachlor_sed', NULL, value = 0.49, min = 0, width = '100%')),
      	column(2, numericInput('alphaNonachlor_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('alphaNonachlor_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # Chlordane
      fluidRow(
      	column(2, h6('Chlordane')),
      	column(2, h6('gammaNonachlor')),
      	column(2, numericInput('gammaNonachlor_sed', NULL, value = 0.5, min = 0, width = '100%')),
      	column(2, numericInput('gammaNonachlor_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('gammaNonachlor_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # Chlordane
      fluidRow(
      	column(2, h6('Chlordane')),
      	column(2, h6('Oxychlordane')),
      	column(2, numericInput('Oxychlordane_sed', NULL, value = 0.23, min = 0, width = '100%')),
      	column(2, numericInput('Oxychlordane_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('Oxychlordane_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # Dieldrin
      fluidRow(
      	column(2, h6('Dieldrin')),
      	column(2, h6('Dieldrin')),
      	column(2, numericInput('Dieldrin_sed', NULL, value = 0.5, min = 0, width = '100%')),
      	column(2, numericInput('Dieldrin_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('Dieldrin_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # DDT
      fluidRow(
      	column(2, h6('DDT')),
      	column(2, h6('op-DDD')),
      	column(2, numericInput('op-DDD_sed', NULL, value = 0.189302326, min = 0, width = '100%')),
      	column(2, numericInput('op-DDD_dis', NULL, value = 9.305665792, min = 0, width = '100%')),
      	column(2, numericInput('op-DDD_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # DDT
      fluidRow(
      	column(2, h6('DDT')),
      	column(2, h6('op-DDE')),
      	column(2, numericInput('op-DDE_sed', NULL, value = 6.704795349, min = 0, width = '100%')),
      	column(2, numericInput('op-DDE_dis', NULL, value = 44.88585023, min = 0, width = '100%')),
      	column(2, numericInput('op-DDE_por', NULL, value = 63.87, min = 0, width = '100%'))
      	),

      # DDT
      fluidRow(
      	column(2, h6('DDT')),
      	column(2, h6('op-DDT')),
      	column(2, numericInput('op-DDT_sed', NULL, value = 1.2, min = 0, width = '100%')),
      	column(2, numericInput('op-DDT_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('op-DDT_por', NULL, value = 15.68, min = 0, width = '100%'))
      	),

      # DDT
      fluidRow(
      	column(2, h6('DDT')),
      	column(2, h6('pp-DDD')),
      	column(2, numericInput('pp-DDD_sed', NULL, value = 3.243651395, min = 0, width = '100%')),
      	column(2, numericInput('pp-DDD_dis', NULL, value = 19.45333669, min = 0, width = '100%')),
      	column(2, numericInput('pp-DDD_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # DDT
      fluidRow(
      	column(2, h6('DDT')),
      	column(2, h6('pp-DDE')),
      	column(2, numericInput('pp-DDE_sed', NULL, value = 44.74623256, min = 0, width = '100%')),
      	column(2, numericInput('pp-DDE_dis', NULL, value = 306.1044638, min = 0, width = '100%')),
      	column(2, numericInput('pp-DDE_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # DDT
      fluidRow(
      	column(2, h6('DDT')),
      	column(2, h6('pp-DDT')),
      	column(2, numericInput('pp-DDT_sed', NULL, value = 1.099302326, min = 0, width = '100%')),
      	column(2, numericInput('pp-DDT_dis', NULL, value = 8.092710587, min = 0, width = '100%')),
      	column(2, numericInput('pp-DDT_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 8')),
      	column(2, numericInput('PCB 8_sed', NULL, value = 0.5, min = 0, width = '100%')),
      	column(2, numericInput('PCB 8_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 8_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 11')),
      	column(2, numericInput('PCB 11_sed', NULL, value = 0.36, min = 0, width = '100%')),
      	column(2, numericInput('PCB 11_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 11_por', NULL, value = 47.65, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 18')),
      	column(2, numericInput('PCB 18_sed', NULL, value = 0.101054884, min = 0, width = '100%')),
      	column(2, numericInput('PCB 18_dis', NULL, value = 13.185837, min = 0, width = '100%')),
      	column(2, numericInput('PCB 18_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 27')),
      	column(2, numericInput('PCB 27_sed', NULL, value = 0.44, min = 0, width = '100%')),
      	column(2, numericInput('PCB 27_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 27_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 28')),
      	column(2, numericInput('PCB 28_sed', NULL, value = 0.166863488, min = 0, width = '100%')),
      	column(2, numericInput('PCB 28_dis', NULL, value = 11.43476661, min = 0, width = '100%')),
      	column(2, numericInput('PCB 28_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 29')),
      	column(2, numericInput('PCB 29_sed', NULL, value = 0.72, min = 0, width = '100%')),
      	column(2, numericInput('PCB 29_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 29_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 31')),
      	column(2, numericInput('PCB 31_sed', NULL, value = 0.13606575, min = 0, width = '100%')),
      	column(2, numericInput('PCB 31_dis', NULL, value = 6.363272245, min = 0, width = '100%')),
      	column(2, numericInput('PCB 31_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 33')),
      	column(2, numericInput('PCB 33_sed', NULL, value = 0.36, min = 0, width = '100%')),
      	column(2, numericInput('PCB 33_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 33_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 37')),
      	column(2, numericInput('PCB 37_sed', NULL, value = 0.42, min = 0, width = '100%')),
      	column(2, numericInput('PCB 37_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 37_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 44')),
      	column(2, numericInput('PCB 44_sed', NULL, value = 0.405351163, min = 0, width = '100%')),
      	column(2, numericInput('PCB 44_dis', NULL, value = 16.2247466, min = 0, width = '100%')),
      	column(2, numericInput('PCB 44_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 49')),
      	column(2, numericInput('PCB 49_sed', NULL, value = 0.5, min = 0, width = '100%')),
      	column(2, numericInput('PCB 49_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 49_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 52')),
      	column(2, numericInput('PCB 52_sed', NULL, value = 0.5, min = 0, width = '100%')),
      	column(2, numericInput('PCB 52_dis', NULL, value = 17.33, min = 0, width = '100%')),
      	column(2, numericInput('PCB 52_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 56')),
      	column(2, numericInput('PCB 56_sed', NULL, value = 0.54, min = 0, width = '100%')),
      	column(2, numericInput('PCB 56_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 56_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 60')),
      	column(2, numericInput('PCB 60_sed', NULL, value = 0.61, min = 0, width = '100%')),
      	column(2, numericInput('PCB 60_dis', NULL, value = 65.32, min = 0, width = '100%')),
      	column(2, numericInput('PCB 60_por', NULL, value = 140.8, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 64')),
      	column(2, numericInput('PCB 64_sed', NULL, value = 0.38, min = 0, width = '100%')),
      	column(2, numericInput('PCB 64_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 64_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 66')),
      	column(2, numericInput('PCB 66_sed', NULL, value = 1.05, min = 0, width = '100%')),
      	column(2, numericInput('PCB 66_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 66_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 70')),
      	column(2, numericInput('PCB 70_sed', NULL, value = 1.35, min = 0, width = '100%')),
      	column(2, numericInput('PCB 70_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 70_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 74')),
      	column(2, numericInput('PCB 74_sed', NULL, value = 0.194457209, min = 0, width = '100%')),
      	column(2, numericInput('PCB 74_dis', NULL, value = 3.470400349, min = 0, width = '100%')),
      	column(2, numericInput('PCB 74_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 77')),
      	column(2, numericInput('PCB 77_sed', NULL, value = 1.12, min = 0, width = '100%')),
      	column(2, numericInput('PCB 77_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 77_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 81')),
      	column(2, numericInput('PCB 81_sed', NULL, value = 1.09, min = 0, width = '100%')),
      	column(2, numericInput('PCB 81_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 81_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 87')),
      	column(2, numericInput('PCB 87_sed', NULL, value = 1.4, min = 0, width = '100%')),
      	column(2, numericInput('PCB 87_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 87_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 95')),
      	column(2, numericInput('PCB 95_sed', NULL, value = 0.77, min = 0, width = '100%')),
      	column(2, numericInput('PCB 95_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 95_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 97')),
      	column(2, numericInput('PCB 97_sed', NULL, value = 0.3636925, min = 0, width = '100%')),
      	column(2, numericInput('PCB 97_dis', NULL, value = 3.681928399, min = 0, width = '100%')),
      	column(2, numericInput('PCB 97_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 99')),
      	column(2, numericInput('PCB 99_sed', NULL, value = 0.617086047, min = 0, width = '100%')),
      	column(2, numericInput('PCB 99_dis', NULL, value = 5.897746631, min = 0, width = '100%')),
      	column(2, numericInput('PCB 99_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 101')),
      	column(2, numericInput('PCB 101_sed', NULL, value = 0.181250006, min = 0, width = '100%')),
      	column(2, numericInput('PCB 101_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 101_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 105')),
      	column(2, numericInput('PCB 105_sed', NULL, value = 0.454006977, min = 0, width = '100%')),
      	column(2, numericInput('PCB 105_dis', NULL, value = 1.599129689, min = 0, width = '100%')),
      	column(2, numericInput('PCB 105_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 110')),
      	column(2, numericInput('PCB 110_sed', NULL, value = 1.601034884, min = 0, width = '100%')),
      	column(2, numericInput('PCB 110_dis', NULL, value = 9.244741774, min = 0, width = '100%')),
      	column(2, numericInput('PCB 110_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 114')),
      	column(2, numericInput('PCB 114_sed', NULL, value = 0.33, min = 0, width = '100%')),
      	column(2, numericInput('PCB 114_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 114_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 118')),
      	column(2, numericInput('PCB 118_sed', NULL, value = 0.275000006, min = 0, width = '100%')),
      	column(2, numericInput('PCB 118_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 118_por', NULL, value = 17.98, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 119')),
      	column(2, numericInput('PCB 119_sed', NULL, value = 0.41, min = 0, width = '100%')),
      	column(2, numericInput('PCB 119_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 119_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 123')),
      	column(2, numericInput('PCB 123_sed', NULL, value = 0.63, min = 0, width = '100%')),
      	column(2, numericInput('PCB 123_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 123_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 126')),
      	column(2, numericInput('PCB 126_sed', NULL, value = 0.38, min = 0, width = '100%')),
      	column(2, numericInput('PCB 126_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 126_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 128')),
      	column(2, numericInput('PCB 128_sed', NULL, value = 0.71, min = 0, width = '100%')),
      	column(2, numericInput('PCB 128_dis', NULL, value = 96.32, min = 0, width = '100%')),
      	column(2, numericInput('PCB 128_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 132')),
      	column(2, numericInput('PCB 132_sed', NULL, value = 0.33, min = 0, width = '100%')),
      	column(2, numericInput('PCB 132_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 132_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 137')),
      	column(2, numericInput('PCB 137_sed', NULL, value = 0.56, min = 0, width = '100%')),
      	column(2, numericInput('PCB 137_dis', NULL, value = 165.6, min = 0, width = '100%')),
      	column(2, numericInput('PCB 137_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 138')),
      	column(2, numericInput('PCB 138_sed', NULL, value = 0.25384615, min = 0, width = '100%')),
      	column(2, numericInput('PCB 138_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 138_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 141')),
      	column(2, numericInput('PCB 141_sed', NULL, value = 0.29, min = 0, width = '100%')),
      	column(2, numericInput('PCB 141_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 141_por', NULL, value = 27.86, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 146')),
      	column(2, numericInput('PCB 146_sed', NULL, value = 1.01, min = 0, width = '100%')),
      	column(2, numericInput('PCB 146_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 146_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 149')),
      	column(2, numericInput('PCB 149_sed', NULL, value = 1.25, min = 0, width = '100%')),
      	column(2, numericInput('PCB 149_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 149_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 151')),
      	column(2, numericInput('PCB 151_sed', NULL, value = 0.215226512, min = 0, width = '100%')),
      	column(2, numericInput('PCB 151_dis', NULL, value = 1.879261719, min = 0, width = '100%')),
      	column(2, numericInput('PCB 151_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 153')),
      	column(2, numericInput('PCB 153_sed', NULL, value = 1.39244, min = 0, width = '100%')),
      	column(2, numericInput('PCB 153_dis', NULL, value = 5.251926401, min = 0, width = '100%')),
      	column(2, numericInput('PCB 153_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 156')),
      	column(2, numericInput('PCB 156_sed', NULL, value = 0.148466047, min = 0, width = '100%')),
      	column(2, numericInput('PCB 156_dis', NULL, value = 0.319787514, min = 0, width = '100%')),
      	column(2, numericInput('PCB 156_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 157')),
      	column(2, numericInput('PCB 157_sed', NULL, value = 0.56, min = 0, width = '100%')),
      	column(2, numericInput('PCB 157_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 157_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 158')),
      	column(2, numericInput('PCB 158_sed', NULL, value = 1.3, min = 0, width = '100%')),
      	column(2, numericInput('PCB 158_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 158_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 167')),
      	column(2, numericInput('PCB 167_sed', NULL, value = 0.74, min = 0, width = '100%')),
      	column(2, numericInput('PCB 167_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 167_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 168')),
      	column(2, numericInput('PCB 168_sed', NULL, value = 0.21, min = 0, width = '100%')),
      	column(2, numericInput('PCB 168_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 168_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 169')),
      	column(2, numericInput('PCB 169_sed', NULL, value = 1.11, min = 0, width = '100%')),
      	column(2, numericInput('PCB 169_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 169_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 170')),
      	column(2, numericInput('PCB 170_sed', NULL, value = 0.330709302, min = 0, width = '100%')),
      	column(2, numericInput('PCB 170_dis', NULL, value = 0.569421342, min = 0, width = '100%')),
      	column(2, numericInput('PCB 170_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 174')),
      	column(2, numericInput('PCB 174_sed', NULL, value = 0.322745, min = 0, width = '100%')),
      	column(2, numericInput('PCB 174_dis', NULL, value = 0.894510598, min = 0, width = '100%')),
      	column(2, numericInput('PCB 174_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 177')),
      	column(2, numericInput('PCB 177_sed', NULL, value = 0.121874884, min = 0, width = '100%')),
      	column(2, numericInput('PCB 177_dis', NULL, value = 0.522629476, min = 0, width = '100%')),
      	column(2, numericInput('PCB 177_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 180')),
      	column(2, numericInput('PCB 180_sed', NULL, value = 0.697543256, min = 0, width = '100%')),
      	column(2, numericInput('PCB 180_dis', NULL, value = 1.495032452, min = 0, width = '100%')),
      	column(2, numericInput('PCB 180_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 183')),
      	column(2, numericInput('PCB 183_sed', NULL, value = 0.112256047, min = 0, width = '100%')),
      	column(2, numericInput('PCB 183_dis', NULL, value = 0.451321306, min = 0, width = '100%')),
      	column(2, numericInput('PCB 183_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 187')),
      	column(2, numericInput('PCB 187_sed', NULL, value = 0.7125, min = 0, width = '100%')),
      	column(2, numericInput('PCB 187_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 187_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 189')),
      	column(2, numericInput('PCB 189_sed', NULL, value = 0.64, min = 0, width = '100%')),
      	column(2, numericInput('PCB 189_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 189_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 194')),
      	column(2, numericInput('PCB 194_sed', NULL, value = 0.19812907, min = 0, width = '100%')),
      	column(2, numericInput('PCB 194_dis', NULL, value = 0.238347374, min = 0, width = '100%')),
      	column(2, numericInput('PCB 194_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 195')),
      	column(2, numericInput('PCB 195_sed', NULL, value = 0.066266, min = 0, width = '100%')),
      	column(2, numericInput('PCB 195_dis', NULL, value = 0.10184514, min = 0, width = '100%')),
      	column(2, numericInput('PCB 195_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 198')),
      	column(2, numericInput('PCB 198_sed', NULL, value = 0.45, min = 0, width = '100%')),
      	column(2, numericInput('PCB 198_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 198_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 199')),
      	column(2, numericInput('PCB 199_sed', NULL, value = 0.68, min = 0, width = '100%')),
      	column(2, numericInput('PCB 199_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 199_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 200')),
      	column(2, numericInput('PCB 200_sed', NULL, value = 0.77, min = 0, width = '100%')),
      	column(2, numericInput('PCB 200_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 200_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 201')),
      	column(2, numericInput('PCB 201_sed', NULL, value = 0.015007186, min = 0, width = '100%')),
      	column(2, numericInput('PCB 201_dis', NULL, value = 0.04712185, min = 0, width = '100%')),
      	column(2, numericInput('PCB 201_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 203')),
      	column(2, numericInput('PCB 203_sed', NULL, value = 1.15, min = 0, width = '100%')),
      	column(2, numericInput('PCB 203_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 203_por', NULL, value = NULL, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 206')),
      	column(2, numericInput('PCB 206_sed', NULL, value = 1.02, min = 0, width = '100%')),
      	column(2, numericInput('PCB 206_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 206_por', NULL, value = 125.7, min = 0, width = '100%'))
      	),

      # PCB
      fluidRow(
      	column(2, h6('PCB')),
      	column(2, h6('PCB 209')),
      	column(2, numericInput('PCB 209_sed', NULL, value = 0.86, min = 0, width = '100%')),
      	column(2, numericInput('PCB 209_dis', NULL, value = NULL, min = 0, width = '100%')),
      	column(2, numericInput('PCB 209_por', NULL, value = NULL, min = 0, width = '100%'))
      	)

    )
    
    out <- div(
      h3('Indicator guild species and sediment contaminant concentrations'), 
      w1,
      h3('Site and environmental data'), 
      w2, 
      h3('Contaminants'), 
      w3
      )
      
  }
  
  if(inptyp == 'File upload'){
    
    w1 <- wellPanel(id = "indicspec", style = "overflow-x:scroll; background-color:#daf1da",
      column(3, downloadButtonRmd('dlbiotatmpl', 'Download template')),
      column(4, fileInput('biotaupl', NULL, accept = '.csv'))
    )
    
    w2 <- wellPanel(id = "envdat", style = "overflow-x:scroll; background-color:#daf1da",    
      column(3, downloadButtonRmd('dlconstantstmpl', 'Download template')),
      column(4, fileInput('constantsupl', NULL, accept = '.csv'))
    )
    
    w3 <- wellPanel(id = "contamdat", style = "overflow-x:scroll; background-color:#daf1da",  
      column(3, downloadButtonRmd('dlcontamtmpl', 'Download template')),
      column(4, fileInput('contamupl', NULL, accept = '.csv'))
    )
    
    w4 <- wellPanel(id = "mcsparmsdat", style = "overflow-x:scroll; background-color:#daf1da",
      column(3, downloadButtonRmd('dlmcsparmstmpl', 'Download template')),
      column(4, fileInput('mcsparmsupl', NULL, accept = '.csv'))
    )
                        
    out <- div(
      h3('Indicator guild species and sediment contaminant concentrations'), 
      w1,
      h3('Site and environmental data'), 
      w2, 
      h3('Contaminants'), 
      w3, 
      h3('MCS parameters'), 
      w4
      )
    
  }
  
  return(out)
  
})
```
```{r}
uiOutput('entry')
```

## Food Web calculations {.tabset .tabset-pills}

### Guild species results summary

```{r}
# calculated and observed concentrations
output$tabsum <- renderTable({indic_sum()})
```
```{r}
column(12, 
  column(4, downloadButtonRmd('dlindicsum', 'Download table'))
)
column(12, 
  tableOutput('tabsum')
)
```

### Plot all species by contaminant

```{r}
output$cntbsaf <- renderUI({

  # input
  contamcalc <- res$contamcalc

  selectInput('cntbsaf', 'Select contaminant:', choices = contamcalc$Chem)
  
})
output$plobsaf <- renderPlot({plobsaf()}, height = 600)
```
```{r}
column(12,  
  column(4, downloadButtonRmd('dlplobsaf', 'Download plot')),
  column(4, uiOutput('cntbsaf'))
)
column(12, 
  plotOutput('plobsaf')
)
```

### All results table

```{r}
output$tabbsaf <- renderDataTable({tabbsaf()})
```
```{r}
column(12, 
  column(4, downloadButtonRmd('dltabbsaf', 'Download table'))
)
column(12, 
  dataTableOutput('tabbsaf')
)
```

## Output summary {.tabset .tabset-pills}

```{r}
# sqo assessment summary
output$sqosum <- renderTable({sqosum()})

# mcs summary table for site linkages
output$mcssum <- renderTable({MCSsum()})

# MCS summary plot for cdf
output$mcspl <- renderPlot({mcspl()}, height = 600, width = 800)

# sediment site linkage values for all simulations
output$mcsres <- renderTable({mcsres()})
```

### SQO assessment summary

```{r}
column(12, 
  column(4, downloadButtonRmd('dlsqosum', 'Download table'))
)
column(12, 
  tableOutput('sqosum')
)
```

### MCS summary of sediment site linkages

```{r}
column(12,
  column(4, downloadButtonRmd('dlmcssum', 'Download table'))
)
column(12,
  tableOutput('mcssum')
)
column(12,
  column(4, downloadButtonRmd('dlmcspl', 'Download plot'))
)
column(12,
  plotOutput('mcspl')
)
```

### Detailed MCS output of sediment site linkages

```{r}
column(12, 
  column(4, downloadButtonRmd('dlmcsres', 'Download table'))
)
column(12, 
  tableOutput('mcsres')
)
```

## Additional output {.tabset .tabset-pills}

### Calculated contaminants

```{r, context = 'server'}
output$calccont <- renderDataTable({res$contamcalc})
```
```{r}
column(12, 
  column(4, downloadButtonRmd('dlcalccont', 'Download table'))
)
column(12, 
  dataTableOutput('calccont')
)
```


